### 2017-01-31 doc/manuscript.Rmd
Removed FDR-corrected numbers in Results

There were `r nrow(dplyr::filter(gee_unadj_df, p.value <= 0.05))` FDR-corrected 
significant associations in the unadjusted GEE model (see `r cite_f('gee_unadj')`) and 
`r nrow(dplyr::filter(gee_adj_df, p.value <= 0.05))` FDR-corrected
significant associations in the adjusted GEE model as shown in `r cite_f('gee_adj')`. 
The majority of associations with beta-cell function measures were attenuated
after full model adjustment, while nearly all associations with insulin
sensitivity remained significant. 
<!--{{ confirm }} Subsequent analysis revealed
that the attenuation with beta-cell function was due primarily to adjustment for
{{ waist? ALT? }}.-->

>>>>

Results from the unadjusted GEE model are shown in `r cite_f('gee_unadj')`) and 
for the adjusted GEE model in `r cite_f('gee_adj')`. 
The majority of associations with beta-cell function measures were attenuated
after full model adjustment, while nearly all associations with insulin
sensitivity remained significant. 
<!--{{ confirm }} Subsequent analysis revealed
that the attenuation with beta-cell function was due primarily to adjustment for
{{ waist? ALT? }}.-->
